### 2016-08-01 Docs/FAQ/faq.tex

  An alternate way to get single-processor timings, when using the GCC
  compilers is to add {\tt -pg} to the compilation flags for both {\tt
    gfortran} and {\tt gcc} (this can be accomplished by setting {\tt
    GPROF := t} in your {\tt GNUmakefile}.  Upon completion, a file
  names {\tt gmon.out} will be produced.  This can be processed by
  {\tt gprof} running

  {\tt~~~ gprof} {\em exec-name}

  where {\em exec-name} is the name of the executable.

>>>>

  An alternate way to get single-processor timings, when using the GCC
  compilers is to add {\tt -pg} to the compilation flags for both {\tt
    gfortran} and {\tt gcc}.  This can be accomplished by setting:
  \begin{verbatim}
    GPROF := t
\end{verbatim}
  in your {\tt GNUmakefile}.  Upon completion, a file
  names {\tt gmon.out} will be produced.  This can be processed by
  {\tt gprof} running

  \begin{verbatim}
    gprof exec-name
\end{verbatim}
  where {\em exec-name} is the name of the executable.  More detailed
  line-by-line timings can be obtained by using the {\tt -l} argument
  to {\tt gprof}.

### 2016-08-01 Docs/makefiles/makefiles.tex

A few files use explicit `{\tt include}' statements to include Fortran
source in other source files.  Any include file locations should be
added to {\tt Fmincludes} variable in the problem's {\tt GNUmakefile}.
This does not occur frequently.  For the case of the {\tt helmeos}
equation of state, this is done automatically in {\tt GMaestro.mak}.

@@

  This variable points to the directory (by default, relative to {\tt
  Microphysics/EOS/}) of the equation of state used for the build.
  Choices that work with \maestro\ are:
  \begin{itemize}
  \item {\tt helmeos}
  \item {\tt gamma\_law\_general}
  \item {\tt multigamma}
  \end{itemize}
  To use an EOS contained in a different location, set the variable {\tt
  EOS\_TOP\_DIR} to point to the directory above the alternate EOS
  directory.

@@

\subsection{Debugging ({\tt print-*})}

@@

>>>>

A few files use explicit `{\tt include}' statements to include Fortran
source in other source files.  Any include file locations should be
added to {\tt Fmincludes} variable in the problem's {\tt GNUmakefile}.
This does not occur frequently.  For the case of the {\tt helmholtz}
equation of state, this is done automatically in {\tt GMaestro.mak}.

@@

  This variable points to the directory (by default, relative to {\tt
  Microphysics/EOS/}) of the equation of state used for the build.
  Choices that work with \maestro\ are:
  \begin{itemize}
  \item {\tt helmholtz}
  \item {\tt gamma\_law\_general}
  \item {\tt multigamma}
  \end{itemize}
  To use an EOS contained in a different location, set the variable {\tt
  EOS\_TOP\_DIR} to point to the directory above the alternate EOS
  directory.

@@

\subsection{Debugging}

\subsubsection{({\tt print-*})}

@@

\subsubsection{{\tt file\_locations}}

Source files are found by searching through the {\tt make} {\tt
  vpath}.  The first instance of the file found in the {\tt vpath}
is used in the build.  To see which files are used and their locations,
do:
\begin{verbatim}
make file_locations
\end{verbatim}

This will also show any files that aren't found.  Some are expected
(e.g., {\tt build\_info.f90} and {\tt probin.f90} are created at
compile time), but other files that are not found could indicate
an incomplete {\tt vpath}.

### 2016-08-01 Docs/runtime_parameters/runtime_parameters.tex

>>>>

\renewcommand{\arraystretch}{1.5}
%
\begin{center}
\begin{longtable}{|l|p{5.25in}|l|}
\caption[ debugging
 parameters.]{ debugging
 parameters.} \label{table:  debugging
 parameters. runtime} \\
%
\hline \multicolumn{1}{|c|}{\textbf{parameter}} &
       \multicolumn{1}{ c|}{\textbf{description}} &
       \multicolumn{1}{ c|}{\textbf{default value}} \\ \hline
\endfirsthead

\rowcolor{tableShade}
\verb= boxlib_fpe_invalid = &  enable floating point exception trapping for invalid & .false. \\
\verb= boxlib_fpe_overflow = &  enable floating point exception trapping for overflow & .false. \\
\rowcolor{tableShade}
\verb= boxlib_fpe_zero = &  enable floating point exception trapping for divide by zero & .false. \\
